Response to reviewers

### 2022-06-07 response/response3.Rmd
addressed the AE comment on the abstract - not sure what they are reading but they are wrong

@@

@@

>>>>

Nothing to respond to here.

@@

Corrected as follows

@@

The abstract does NOT promise an exploratory analysis for longitudinal data. It mentions that one of the purposes of this textbook data is to use it to teach exploratory analysis of longitudinal data. Similarly, it also states that the data is useful for teaching modeling. Both of these are beyond the scope of this paper. They are still important to keep because it makes the reader aware of why this data is useful and important. No change to abstract was made.
